\bf A Hierarchical Model for Heterogenous Reliability Field Data

### 2018-03-30 paper/m-lb-m-technometrics.tex

\section{Introduction}
\subsection{Motivation}
Consumers have an interest in accurate assessment of product reliability}. Toward this end, there usually is a need for models that can accommodate common failure patterns and methods which can make the most of available data and properly account for uncertainty. Doing these things well enables good decision-making in matters related to product life, including purchase decisions and contingency planning.
%While computationally convenient, simple lifetime models can fail at each of these.

@@

\begin{itemize}
\item Making purchase decisions from among different suppliers of the components or subsystems.
\item Making predictions for the number of needed replacement components or subsystems for spare part provisioning.
\end{itemize}

@@

The GLFP model has a meaningful parameterization and accommodates lifetime data with both early and wearout failures.  Unfortunately, it can require a lot of data to fit due to the model's complexity. When multiple sources of information are available, partial pooling, accomplished via hierarchical modeling, can reduce the amount of data required to produce stable parameter estimates. When multiple sub-populations are of interest, comparisons based on separate, unrestricted GLFP model fits will be limited to those products with sufficient data. As we will show, hierarchical modeling of the GLFP parameters allows for borrowing of information across sub-populations which imposes ``soft'' constraints on model parameters. This enables estimation of the lifetime distribution for all sub-populations via shrinkage toward a ``pooled" model, with the degree of shrinkage inversely related to the amount of sub-population specific information. We demonstrate the computation of various quantities of interest while comparing reliability across populations using numerical integration over the posterior distribution with samples obtained via Markov Chain Monte Carlo (MCMC).

@@

\subsection{Model selection}
From the point of view of a consumer or purchaser, the goal of an analysis such as this is may be to rate manufacturers and/or to inform future purchases based on predicted product performance. In this case, we should choose the model that will provide the most accurate prediction for future units of previously observed products. One appropriate criterion for model selection, then, is the log pointwise predictive density (lpd),

\begin{align*}
\mbox{lpd} &= \sum_{g=1}^G \sum_{i=1}^{n_g} \log[p(t_{new,g,i}|t, t^L, c)] \\
&= \sum_{g=1}^G \sum_{i=1}^{n_g} \log \left[ \int p(t_{new,g, i}|\theta) p(\theta|t,t^L,c) d\theta \right].
\end{align*}
\noindent Using this criterion, we should choose the model with the highest expected lpd (elpd) for a new data set $\{t_{new,g,i}:g=1,\ldots,G; i=1,\ldots,n_g\}$. Notationally suppressing the conditioning on $t^L$ and $c$,
\begin{equation}
\mbox{elpd} = \op{E}_h \mbox{lpd} = \sum_{g=1}^G \sum_{i=1}^{n_g} \int \log [p(t_{new, g, i}|t)] h(t_{new,g,i}) d t_{new,g,i},
\label{elpd}
\end{equation}
where $h$ is a density for the true distribution of $t_{new,g,i}$. Although $h$ is unknown, leave-one-out cross-validation provides a robust estimator:
\begin{equation}
\widehat{\text{elpd}} = \sum_{g=1}^G \sum_{i=1}^{n_g} \log [p(t_{g,i}|t_{-(g,i)})].
\label{loo-est}
\end{equation}
The \texttt{R} package, \texttt{loo} \citep{loo}, computes an approximation of (\ref{loo-est}) provided that the observations $t_i$ are conditionally independent. It employs an importance sampling method that uses $S$ saved MCMC draws to compute smoothed importance weights, $w_{i,s}$, approximating $\log [p(t_{g,i}|t_{-(g,i)})]$ with $\sum_{i=1}^S w_{i,s} p(t_{g,i})/\sum_{s=1}^S w_{i,s}$. In addition to providing an estimate of (\ref{elpd}), their method also produces a standard error based on an asymptotic result. For details, refer to \cite{vehtari}.
%When $n$ is large, the distribution of the elpd is approximately normal and different models can be compared statistically. 
% To statistically compare the GLFP Models, we estimated the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  As outlined in Vehtari et. al, the predictive accuracy from a fitted Bayesian model can be estimated simply with posterior draws of the model parameters rather than re-fitting the model with different data sets \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior samples with data point $i$ removed.  
% The final expected log point-wise predictive density (elpd) is the sum over all observations (elpd $=\sum{\log p(y_i|y_{-i})}$).

@@

\begin{figure}[H]
{\centering
\includegraphics[width=\textwidth]{single-drive-4-Models-ex}}
\caption{Posterior median of the proportion failing as a function of time under Models 1-4 for sample of drive-models, with axes scales as for Weibull probability plotting.  The solid step function is the adjusted K-M estimate.}
\label{fig:mod_comp_leg}
\end{figure}

@@

\begin{figure}
\begin{table}[H]
\centering
\begin{tabular}{rrrrrrr}
  \hline
 & $\widehat{\text{elpd}}$ \ & Difference in $\widehat{\text{elpd}}$ \ & SE of the Difference \\ 
  \hline
Model 4 & -13309.5 & 40.7 & 11.3 \\ 
Model 3 & -13350.2 & 458.8 & 31.0  \\ 
Model 2 & -13809.0 & 3674.6 & 96.2 \\ 
Model 1 & -17483.6  \\ 
   \hline
\end{tabular}
\caption{Expected Log Pointwise Predictive Density (elpd) for each model specification.  Each model is compared to the more parsimonious model below.  The estimated difference of expected leave-one-out prediction errors between the two models, as well as the standard error of the difference, is also presented.}
\label{table:2}
\end{table}
\end{figure}

>>>>

\section{Introduction}
\subsection{Motivation}
Consumers have an interest in accurate assessment of product reliability. Toward this end, there usually is a need for models that can accommodate common failure patterns and methods which can make the most of available data and properly account for uncertainty. Doing these things well enables good decision-making in matters related to product life, including purchase decisions and contingency planning.
%While computationally convenient, simple lifetime models can fail at each of these.

@@

\begin{itemize}
\item Making purchase decisions from among different suppliers of the components or subsystems.
\item Making inference about the lifetime distribution of products with few observed failures.
\item Making predictions for the number of needed replacement components or subsystems for spare part provisioning.
\end{itemize}

@@

The GLFP model has a meaningful parameterization and accommodates lifetime data with both early and wearout failures.  Unfortunately, it can require a lot of data to fit due to the model's complexity.  For example, clothing and electronic manufacturers, as well as pharmaceutical companies, often test products that rarely fail, even under accelerated testing.  With few observed failures, fitting multi-parameter models can be unstable or impossible using standard estimation methods.  When multiple sources of information are available, partial pooling, accomplished via hierarchical modeling, can reduce the amount of data required to produce stable parameter estimates. When multiple sub-populations are of interest, comparisons based on separate, unrestricted GLFP model fits will be limited to those products with sufficient data. As we will show, hierarchical modeling of the GLFP parameters allows for borrowing of information across sub-populations which imposes ``soft'' constraints on model parameters. This enables estimation of the lifetime distribution for all sub-populations via shrinkage toward a ``pooled" model, with the degree of shrinkage inversely related to the amount of sub-population specific information. We demonstrate the computation of various quantities of interest while comparing reliability across populations using numerical integration over the posterior distribution with samples obtained via Markov Chain Monte Carlo (MCMC).

@@

\subsection{Model selection}
From the point of view of a consumer or purchaser, the goal of an analysis such as this is may be to rate manufacturers and/or to inform future purchases based on predicted product performance. Therefore, we should compare model specifications based on accurate prediction for future units of previously observed products.  Leave-one-out cross-validation (LOO) is a method to estimate out-of-sample predictive accuracy using
posterior draws from a fitted model.  The log pointwise predictive density (lpd), is one method to quantify predictive accuracy,

\begin{align*}
\mbox{lpd} &= \sum_{g=1}^G \sum_{i=1}^{n_g} \log[p(t_{new,g,i}|t, t^L, c)] \\
&= \sum_{g=1}^G \sum_{i=1}^{n_g} \log \left[ \int p(t_{new,g, i}|\theta) p(\theta|t,t^L,c) d\theta \right].
\end{align*}
\noindent Using this criterion, we should choose the model with the highest expected lpd (elpd) for a new data set $\{t_{new,g,i}:g=1,\ldots,G; i=1,\ldots,n_g\}$. Notationally suppressing the conditioning on $t^L$ and $c$,
\begin{equation}
\mbox{elpd} = \op{E}_h \mbox{lpd} = \sum_{g=1}^G \sum_{i=1}^{n_g} \int \log [p(t_{new, g, i}|t)] h(t_{new,g,i}) d t_{new,g,i},
\label{elpd}
\end{equation}
where $h$ is a density for the true distribution of $t_{new,g,i}$. Although $h$ is unknown, leave-one-out cross-validation provides a robust estimator:
\begin{equation}
\widehat{\text{elpd}} = \sum_{g=1}^G \sum_{i=1}^{n_g} \log [p(t_{g,i}|t_{-(g,i)})].
\label{loo-est}
\end{equation}
The \texttt{R} package, \texttt{loo} \citep{loo}, computes an approximation of (\ref{loo-est}) provided that the observations $t_i$ are conditionally independent. It employs an importance sampling method that uses $S$ saved MCMC draws to compute smoothed importance weights, $w_{i,s}$, approximating $p(t_{g,i}|t_{-(g,i)})$ with $\sum_{s=1}^S w_{i,s} p(t_{g,i})/\sum_{s=1}^S w_{i,s}$. In addition to providing an estimate of (\ref{elpd}), their method also produces a standard error based on an asymptotic result. For details, refer to \cite{vehtari}.
%When $n$ is large, the distribution of the elpd is approximately normal and different models can be compared statistically. 
% To statistically compare the GLFP Models, we estimated the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  As outlined in Vehtari et. al, the predictive accuracy from a fitted Bayesian model can be estimated simply with posterior draws of the model parameters rather than re-fitting the model with different data sets \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior samples with data point $i$ removed.  
% The final expected log point-wise predictive density (elpd) is the sum over all observations (elpd $=\sum{\log p(y_i|y_{-i})}$).

@@

\begin{figure}[H]
{\centering
\includegraphics[width=\textwidth]{single-drive-4-Models-ex-v2}}
\caption{Posterior median of the proportion failing as a function of time under Models 1-4 for sample of drive-models, with axes scales as for Weibull probability plotting.  The solid step function is the adjusted K-M estimate.}
\label{fig:mod_comp_leg}
\end{figure}

@@

\begin{figure}
\begin{table}[H]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & $\widehat{\text{elpd}}$ \ & Difference in $\widehat{\text{elpd}}$ \ & SE of the Difference & Effective No. Parameters\\ 
  \hline
Model 4 & -13309.5 & 40.7 & 11.3 & 92.5 \\ 
Model 3 & -13350.2 & 458.8 & 31.0 & 68.8 \\ 
Model 2 & -13809.0 & 3674.6 & 96.2 & 49.6 \\ 
Model 1 & -17483.6 &  &  & 4.3 \\
   \hline
\end{tabular}
\caption{Expected Log Pointwise Predictive Density (elpd) for each model specification.  Each model is compared to the more parsimonious model below.  The estimated difference of expected leave-one-out prediction errors between the two models, the standard error of the difference, and the effective number of parameters in each model, is also presented.}
\label{table:2}
\end{table}
\end{figure}
